---
title: "2025 WFU Faculty Survey"
author: "Joddy Marchesoni"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preparing tables and charts

## Load libraries and data

```{r include=FALSE}
# Load libraries
library(tidyverse)
library(dplyr)
library(ggplot2)

# Load the data
load("survey.RData")
```

## Table generation functions

```{r include=FALSE}
make_table_var <- function(data, var, sort) {
  table <- data %>% filter(!is.na(var)) %>% group_by(var) %>% summarize(total=n())
  if(sort) {
    table <- table %>% arrange(var)
  }
}

make_table <- function(data, q, sort) {
  table <- data %>% filter(question == q) %>% group_by(question,item) %>% summarize(total=n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
  if(sort) {
    table <- table %>% arrange(desc(total))
  }
}
```

## Generate results summary tables

```{r include=FALSE}
# Generate summaries for result tables
t_finished <- quant_survey %>% filter(!is.na(finished)) %>% group_by(finished) %>% summarize(total=n())
t_finished$finished <- c("Incomplete", "Complete")
t_finished <- t_finished %>% arrange(desc(total))

t_faculty_body <- quant_survey %>% filter(!is.na(faculty.body)) %>% group_by(faculty.body) %>% summarize(total=n())
t_faculty_body <- t_faculty_body %>% arrange(faculty.body)

t_faculty_position <- quant_survey %>% filter(!is.na(faculty.position)) %>% group_by(faculty.position) %>% summarize(total=n())
t_faculty_position <- t_faculty_position %>% arrange(desc(total))

t_faculty_served <- quant_survey %>% filter(!is.na(faculty.served)) %>% group_by(faculty.served) %>% summarize(total=n())

t_research_types <- plot_survey %>% filter(question == "research") %>% group_by(question,item) %>% summarize(total=n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_research_types <- t_research_types %>% arrange(desc(total))

t_research_types_other <- qual_survey_long %>% filter(question == "research_type_other") %>% select(-question) %>% arrange(response)

t_tools <- plot_survey %>% filter(question == "tools") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_tools <- t_tools %>% arrange(desc(total))

t_tools_other <- qual_survey_long %>% filter(question == "tools_other") %>% select(-question) %>% arrange(response)

t_collect <- plot_survey %>% filter(question == "collect") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_collect <- t_collect %>% arrange(desc(total))

t_collect_other <- qual_survey_long %>% filter(question == "collect_other") %>% select(-question) %>% arrange(response)

t_create <- plot_survey %>% filter(question == "create") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_create <- t_create %>% arrange(desc(total))

t_create_other <- qual_survey_long %>% filter(question == "create_other") %>% select(-question) %>% arrange(response)

t_store <- plot_survey %>% filter(question == "store") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_store <- t_store %>% arrange(desc(total))

t_store_other <- qual_survey_long %>% filter(question == "store_other") %>% select(-question) %>% arrange(response)

t_funders_require_dmp <- quant_survey %>% filter(!is.na(funders.require_dmp)) %>% group_by(funders.require_dmp) %>% summarize(total=n())

t_funders_require_dmp_other <- qual_survey_long %>% filter(question == "dmsp_required_not_sure") %>% select(-question) %>% arrange(response)

t_funding <- plot_survey %>% filter(question == "funding") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_funding <- t_funding %>% arrange(desc(total))

t_funding_other <- qual_survey_long %>% filter(question == "funding_type_other") %>% select(-question) %>% arrange(response)

t_submit_repo <- quant_survey %>% filter(!is.na(submit.repo)) %>% group_by(submit.repo) %>% summarize(total=n())

t_submit_repo_other <- qual_survey_long %>% filter(question == "submit_repo_other") %>% select(-question) %>% arrange(response)

t_repo <- plot_survey %>% filter(question == "repo") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_repo <- t_repo %>% arrange(desc(total))

# t_repo_other <- qual_survey_long %>% filter(question == "repos_other") %>% select(-question) %>% arrange(response)

t_concerns <- plot_survey %>% filter(question == "concerns") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_concerns <- t_concerns %>% arrange(desc(total))

t_concerns_other <- qual_survey_long %>% filter(question == "concerns_other") %>% select(-question) %>% arrange(response)

t_proc <- plot_survey %>% filter(question == "proc") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_proc <- t_proc %>% arrange(desc(total))

t_proc_other <- qual_survey_long %>% filter(question == "proc_other") %>% select(-question) %>% arrange(response)

t_resources <- plot_survey %>% filter(question == "resources") %>% group_by(question, item) %>% summarize(total = n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_resources <- t_resources %>% arrange(desc(total))

t_resources_other <- qual_survey_long %>% filter(question == "resources_other") %>% select(-question) %>% arrange(response)

t_lib <- plot_survey %>% filter(question == "lib") %>% group_by(question, item) %>% summarize(total=n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_lib <- t_lib %>% arrange(desc(total))

t_lib_other <- qual_survey_long %>% filter(question == "lib_other") %>% select(-question) %>% arrange(response)

t_workshops <- plot_survey %>% filter(question == "workshops") %>% group_by(question, item) %>% summarize(total=n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)
t_workshops <- t_workshops %>% arrange(desc(total))

t_workshops_other <- qual_survey_long %>% filter(question == "workshops_other") %>% select(-question) %>% arrange(response)

t_w_timing <- plot_survey %>% filter(question == "w_timing") %>% group_by(question, item) %>% summarize(total=n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)

t_w_timing_other <- qual_survey_long %>% filter(question == "workshop_timing_other") %>% select(-question) %>% arrange(response)

t_w_time_day <- plot_survey %>% filter(question == "w_time_day") %>% group_by(question, item) %>% summarize(total=n()) %>% type.convert(as.is=TRUE) %>% ungroup() %>% select(-question)

t_workshop_modality <- quant_survey %>% filter(!is.na(workshop.modality)) %>% group_by(workshop.modality) %>% summarize(total=n())

# t_prevented_attending_w <- qual_survey_long %>% filter(question == "prevented_attending_w") %>% select(-question) %>% arrange(response)

# t_additional_comments <- qual_survey_long %>% filter(question == "additional_comments") %>% select(-question) %>% arrange(response)

# t_new_developments <- qual_survey_long %>% filter(question == "new_developments") %>% select(-question) %>% arrange(response)
```

## Load qualitative data

```{r echo=FALSE}
library(readxl)

# Load in the qualitative software table for other software
tools_other <- read_xlsx("qual_software_tools.xlsx")

# Load in the other qual codes
quals <- read_xlsx("free_response_data.xlsx")
highlights <- read_xlsx("highlights.xlsx")

prevented_workshop <- quals %>% filter(Question == "what prevented you from attending a workshop") %>% select(-Question) %>% rename( item = "Code", total = "Frequency") %>% arrange(desc(total))
funding_agencies <- quals %>% filter(Question == "funding agencies") %>% select(-Question) %>% rename( item = "Code", total = "Frequency") %>% arrange(desc(total))
repo_other <- quals %>% filter(Question == "repositories") %>% select(-Question) %>% rename( item = "Code", total = "Frequency") %>% arrange(desc(total))


new_developments <- highlights %>% filter(question == "new_developments") %>% select(-question)
additional_comments <- highlights %>% filter(question == "additional_comments") %>% select(-question)
```

## Prepare tools data

```{r echo=FALSE}
if(!is.null(tools_other$`Software Tools`)) {
  tools_other <- tools_other %>% rename( item = "Software Tools", total = "Frequency")
}

# Combine it with the main tools table and add category column
t_tools_all <- rbind(t_tools, tools_other)
t_tools_all <- t_tools_all %>% slice(-14)

categories <- data.frame(category = c("Productivity",
"Productivity",
"Data storage",
"Multimedia",
"Writing and lit review",
"AI tools",
"Data storage",
"Surveys",
"Programming",
"Writing and lit review",
"Programming",
"Collaboration",
"Data analysis",
"Qualitative analysis",
"Data analysis",
"Data analysis",
"GIS",
"Qualitative analysis",
"Collaboration",
"Programming",
"Mathematics",
"Mathematics",
"Writing and lit review",
"Data analysis",
"Multimedia",
"Productivity",
"Data analysis",
"Multimedia",
"Data analysis",
"Programming",
"Writing and lit review",
"Writing and lit review",
"Multimedia",
"Multimedia",
"Multimedia",
"Programming",
"Data storage",
"Programming",
"Multimedia",
"Data analysis",
"Multimedia",
"Data analysis",
"Writing and lit review",
"Data analysis",
"Data analysis",
"Data analysis",
"Data analysis",
"Surveys",
"Writing and lit review",
"Qualitative analysis",
"Mathematics",
"Writing and lit review",
"Data analysis",
"Data analysis",
"Programming",
"Data analysis",
"Data analysis",
"Multimedia",
"Data analysis",
"Data storage"))

# Reduce the responses down to a small number of categories by adding a column and then summarizing
t_tools_all <- cbind(t_tools_all, categories)
t_tools_all$category <- as.factor(t_tools_all$category)
t_tools_all <- t_tools_all %>% rename(item = "category", tools = "item")

t_tools_categories <- t_tools_all %>% group_by(item) %>% summarize(total = sum(total), tools = str_c(tools, collapse = ", ")) %>% type.convert(as.is=TRUE) %>% ungroup()
t_tools_categories <- t_tools_categories %>% arrange(desc(total))

```

## Make remaining qualitative summary tables

```{r echo=FALSE}
# Making the other qual tables
t_additional_comments <- additional_comments
t_funding_agencies <- funding_agencies
t_new_developments <- new_developments
t_prevented_attending_w <- prevented_workshop
t_repo_other <- repo_other
```

## Table and chart functions

```{r echo=FALSE}
# Load the table libraries
library(gt)
library(gtExtras)
library(treemapify)
library(forcats)

# Set visualization variables
style_colors <- scale_fill_brewer(palette = "Set3")
no_color <- scale_fill_manual(values = rep("#bc80bd", 50))
no_grid <- theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
text_size <- theme(text=element_text(size=16))

# Functions for visualization
tablifier <- function(table, title) {
  table %>% gt() %>% tab_header(title = title) %>% tab_options(table.align = "left", column_labels.hidden = TRUE, table.font.size = 16) %>% cols_align(align = "left")
}

tablifier_bar <- function(table, title, col) {
  col <- enquo(col)
  bar <- table %>% select(!!col)
  table %>% gt() %>% tab_header(title = title) %>% tab_options(table.align = "left", column_labels.hidden = TRUE, table.font.size = 16) %>% cols_align(align = "left") %>% gt_plt_bar(column = !!bar, keep_column = TRUE, color = "#bc80bd", width=60)
}

treemapifier <- function(data, label) {
  data %>% ggplot(aes(area=total, fill=item, label=item)) +
  geom_treemap() +
  geom_treemap_text() +
  labs(fill = label) +
  text_size +
  style_colors
}

treemapifier_v <- function(data, var, label) {
  data %>% ggplot(aes(area=total, fill=var, label=var)) +
  geom_treemap() +
  geom_treemap_text() +
  labs(fill = label) +
  text_size +
  style_colors
}

bar_charter <- function(data, label, color) {
  data %>% mutate(reorder = fct_reorder(item, total)) %>% ggplot(aes(x=reorder, y=total, fill=reorder)) +
  geom_col(show.legend=FALSE) +
  labs(title = NULL,
       x = NULL,
       y = NULL) + 
  theme_minimal() +
  text_size +
  color +
  no_grid +
  coord_flip()
}

bar_charter_v <- function(data, label, color, var) {
  data %>% mutate(reorder = fct_reorder(var, total)) %>% ggplot(aes(x=reorder, y=total, fill=reorder)) +
  geom_col(show.legend=FALSE) +
  labs(title = NULL,
       x = NULL,
       y = NULL) + 
  theme_minimal() +
  text_size +
  color +
  no_grid +
  coord_flip()
}
```

# Faculty Survey Results

## Demographics

```{r echo=FALSE}
tablifier(t_finished, "Complete responses")
```

```{r echo=FALSE}
bar_charter_v(t_finished, "Complete responses", style_colors, t_finished$finished)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_faculty_body, "Faculty body")
# tablifier_bar(t_faculty_body, "Faculty body", t_faculty_body$total)
treemapifier_v(t_faculty_body, t_faculty_body$faculty.body, "Faculty body")
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_faculty_position, "Faculty position")
treemapifier_v(t_faculty_position, t_faculty_position$faculty.position, "Faculty position")
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_faculty_served, "Years served as Wake faculty")
bar_charter_v(t_faculty_served, "Years served as Wake faculty", style_colors, t_faculty_served$faculty.served)
```

------------------------------------------------------------------------

## Conducting Research

```{r echo=FALSE}
tablifier(t_research_types, "What broad type of research do you conduct?")
treemapifier(t_research_types, "Research type")
```

------------------------------------------------------------------------

```{r echo=FALSE}
# Decided to combine qual and quant data for this question into one
# tablifier(t_tools, "What digital tools or software do you use in your research?")
# bar_charter(t_tools, "Research tool", no_color)
# tablifier(t_tools_other, "Other tools used")
```

```{r echo=FALSE}
tablifier(t_tools_categories, "What digital tools or software do you use in your research?")
# bar_charter(t_tools_categories, "Research tool", style_colors)
treemapifier(t_tools_categories, "Software usage")
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_collect, "What type of data do you collect?")
treemapifier(t_collect, "Data type collected")
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_create, "What files do you create while conducting your research?")
treemapifier(t_create, "File type created")
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_store, "Where do you store your research project files?")
bar_charter(t_store, "Data storage platform", no_color)
```

------------------------------------------------------------------------

## Funding and Repositories

```{r echo=FALSE}
tablifier(t_submit_repo, "Have you ever submitted your data to a repository?")
# treemapifier_v(t_submit_repo, t_submit_repo$submit.repo, "Submitted to repository")
bar_charter_v(t_submit_repo, "Have you ever submitted your data to a repository?", style_colors, t_submit_repo$submit.repo)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_funding, "What types of research funding have you received?")
treemapifier(t_funding, "Research funding type received")
tablifier(t_funding_agencies, "Agencies for federally-funded research")
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_funders_require_dmp, "Do any of your current funders require a Data Management and Sharing Plan?")
bar_charter_v(t_funders_require_dmp, "Data Management and Sharing Plan required", style_colors, t_funders_require_dmp$funders.require_dmp)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_repo, "To which repositories did you submit your data?")
treemapifier(t_repo, "Repositories used")
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_resources, "Which resources have you used to complete your DMSP?")
bar_charter(t_resources, "Resources used to complete DMSP", color=style_colors)
```

------------------------------------------------------------------------

## Research Support

```{r echo=FALSE}
tablifier(t_concerns, "What concerns do you have about managing and preserving your digital research materials?")
bar_charter(t_concerns, "Concern about managing and preserving research materials", style_colors)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_proc, "Which elements of the research process do you find most challenging?")
bar_charter(t_proc, "Most challenging element of research process", no_color)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_lib, "Which ZSR library services have you used to support your research?")
bar_charter(t_lib, "ZSR library services used", style_colors)
```

------------------------------------------------------------------------

## Workshops

```{r echo=FALSE}
tablifier(t_workshops, "Which workshops would you be most likely to attend?")
bar_charter(t_workshops, "Interest in workshop", no_color)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_w_timing, "What is your ideal timing for workshops?")
bar_charter(t_w_timing, "Workshop timing", style_colors)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_w_time_day, "At which point during the day are you most likely to attend a library workshop?")
bar_charter(t_w_time_day, "Workshop time of day", style_colors)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_workshop_modality, "Would you prefer in-person or virtual workshops?")
bar_charter_v(t_workshop_modality, "In-person or virtual workshop", style_colors, t_workshop_modality$workshop.modality)
```

------------------------------------------------------------------------

```{r echo=FALSE}
tablifier(t_prevented_attending_w, "What has prevented you from attending workshops in the past?")
```

------------------------------------------------------------------------

## New developments

**I. Enhanced Access to Digital Resources & Tools:**

- **Performing Arts:** A strong demand exists for institutional subscriptions to high-quality streaming services for live theatre and dance, similar to "Digital Theatre plus" and "National Theatre at Home."

- **Research Databases & Journals:** Faculty in Finance and Economics specifically request access to more leading journals and relevant databases, as well as economics blogs (e.g., on Substack).

- **Archival Access:** There's a desire for expanded access to British newspaper archives, such as The London Times and Spectator.

- **Software & Platforms:** Requests include:

<!-- -->

- **Overleaf Premium Subscription:** To provide a university-wide license, similar to existing departmental ones.

- **BioRender License:** For creating scientific figures and illustrations.

- **Tableau & NVivo:** Access to data visualization and qualitative data analysis software, potentially through institutional licenses or virtual labs.

- **AI Tools:** Interest in a "Plus version for ChatGPT" suggests a need for advanced AI capabilities for research and productivity.

**II. Support for Digital Scholarship & Research Methodologies:**

- **Digital Humanities:** This is a significant area, with requests for:

<!-- -->

- Training in identifying and using useful tools for text analysis, mapping, network analysis, and TEI coding.

- General "Digital Humanities training."

<!-- -->

- **Research Workflow & Transparency:**

<!-- -->

- Support for **pre-registering studies** in psychology, indicating a move towards more transparent and rigorous research practices.

- Guidance on **systematic review tools**, as the technology in this area is rapidly improving. The library could help researchers stay informed of the latest tools.

<!-- -->

- **Data Management & Visualization:**

<!-- -->

- New data visualization tools, tips, and techniques.

- An introductory **GIS workshop** is explicitly requested.

- Need for **enhanced cloud storage** to support research data.

<!-- -->

- **Transcription Services:** Programs/software that can transcribe audio files are needed across disciplines, particularly in music for score cleaning and historical document transcription, and for language transcriptions.

**III. Capacity Building & Skill Development:**

- Respondents express a need for support in developing skills for creating **online experiences** (courses, content presentation), including guidance on sharing and organizing digital information. This highlights a need for training and confidence-building in digital pedagogy and content creation.

- The request for help with "Norwegian Art Song Anthology" (music discipline) underscores a need for specialized support in dealing with historical documents, score cleaning, and language transcriptions, indicating a broader need for discipline-specific expertise and resources within the library.

## Additional comments

### **Positive Feedback & Staff Recognition**

\

- Overwhelmingly positive sentiment; feeling "super supported" and well-served.

- **Subject librarians** lauded for purchases and course support.

- Specific shout-outs to **Colleen Foy, Hu, Tanya, and Kathy Shields** for exceptional help with data, archives, and purchases.

- ILL (Interlibrary Loan) described as a "godsend."

- Library appreciated as a productive change of pace/environment.

------------------------------------------------------------------------

### **Resource & Access Requests**

\

- **More digital content:** German newspapers, French psychology and humanities journals, deeper digital theatre and dance archives.

- **Increased budget:** For books and journals.

- **Physical holdings:** Desire for more physical books and greater room/access for them.

- **New software/tools:** Subscription to **EndNote**, resources for **AI tools**.

- **Newspaper archives:** More access, currently self-funding.

------------------------------------------------------------------------

### **Areas for Improvement & Collaboration**

\

- **Website design:** Needs to be more research-focused, less geared toward undergraduates.

- **Software access/training:** Tutorials/workshops needed for existing software (e.g., MaxQDA) to increase awareness and usability; issues with MaxQDA VPN reliance and collaboration.

- **Collaboration:** Work with WFU IS and CAT to capture expertise and prevent redundancy.

- **Database organization:** Negative feedback on new database organization; missed easy access to encyclopedias, WorldCat, and major general databases on the homepage.

- **Advocacy:** Suggestion for library involvement in academic freedom and resisting book banning.

- **Facilitation:** Even if not providing services directly, act as a facilitator for finding external services.
